Technical Report

### 2017-10-30 fully-abstract-comp/technical-report.tex
moved ownership to pure regions only.

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\pureReg}{\mathrm{pure}}
\newcommand{\normalReg}{\mathrm{normal}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\[
  \World = \RegionName \parfun 2 \times \Region
\]
where $\RegionName = \nats$
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pureReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normalReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
  \end{array} \right.
\]
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \uplus (j,\normalReg,\var{sm}) = & (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (1,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\uplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.

>>>>

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\pure}{\mathrm{pure}}
\newcommand{\pureo}{\mathrm{pure\_owned}}
\newcommand{\normReg}{\mathrm{normal}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\pureo$-regions.
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (\normReg,\var{sm}) \oplus (\normReg,\var{sm}) =  & \; (\normReg,\var{sm}) \\
  (\pureo,\var{sm}) \oplus (\pure,\var{sm}) = & \; (\pure,\var{sm}) \oplus (\pureo,\var{sm})\\
                                           =  & \; (\pureo,\var{sm}) \\
  (\pure,\var{sm}) \oplus (\pure,\var{sm}) =  & \; (\pure,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\oplus$ is not defined when both sides are a $\pureo$-region. It is further not defined if the two sides do not agree on region type and state machine. Here $\var{sm}$ is the state machine of the region.
